### 2018-03-16 paper/5-implementations.tex
More Bazel stuff

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Determine whether a trace is relevant to the current state
traceMatch :: (Monad m, Eq k) => (k -> Hash v -> m Bool) -> k -> [Trace k v] -> m [Hash v]
traceMatch check key ts = mapMaybeM f ts
    where f (Trace k dkv v) = do
                b <- return (key == k) &&^ allM (uncurry check) dkv
                return $ if b then Just v else Nothing
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Recursive dependency strategy
recursive
    :: Eq k => (k -> (k -> State (Store i k v, [k]) v) -> State (Store i k v, [k]) (v, [k]) -> State (Store i k v, [k]) ())
    -> Build Monad i k v
recursive process task key store = fst $ execState (ensure key) (store, [])
    where
        ensure key = do
            let fetch k = do ensure k; gets (getValue k . fst)
            done <- gets snd
            when (key `notElem` done) $ do
                modify $ \(s, done) -> (s, key:done)
                case trackM task fetch key of
                    Nothing -> return ()
                    Just act -> process key fetch act
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system
shake :: (Eq k, Hashable v) => Build Monad [Trace k v] k v
shake = recursive $ \key fetch act -> do
    traces <- gets (getInfo . fst)
    poss <- traceMatch (\k v -> (==) v . hash <$> fetch k) key traces
    current <- gets (getHash key . fst)
    when (current `notElem` poss) $ do
        (v, ds) <- act
        modify $ \(s, done) ->
            let t = Trace key [(d, getHash d s) | d <- ds] (getHash key s)
            in (putInfo (t : getInfo s) (putValue key v s), done)

@@

Now we have seen all three dependency schemes, we can reuse , we can directly reuse \hs{topological} to define \Bazel. Furthermore, as \Bazel is a tracing build system, we can reuse \hs{Trace} and \hs{traceMatch}, as part of the \hs{Traces} type. We define \Bazel as:

>>>>

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Determine whether a trace is relevant to the current state
traceMatch :: (Monad m, Eq k) => (k -> Hash v -> m Bool) -> k -> [Trace k v] -> m [Hash v]
traceMatch check key ts = mapMaybeM f ts
    where f (Trace k dkv v) = do
                b <- return (key == k) &&^ allM (uncurry check) dkv
                return $ if b then Just v else Nothing
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Recursive dependency strategy
recursive
    :: Eq k => (k -> (k -> State (Store i k v, [k]) v) -> State (Store i k v, [k]) (v, [k]) -> State (Store i k v, [k]) ())
    -> Build Monad i k v
recursive process task key store = fst $ execState (ensure key) (store, [])
    where
        ensure key = do
            let fetch k = do ensure k; gets (getValue k . fst)
            done <- gets snd
            when (key `notElem` done) $ do
                modify $ \(s, done) -> (s, key:done)
                case track task fetch key of
                    Nothing -> return ()
                    Just act -> process key fetch act
\end{minted}
\vspace{1mm}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system
shake :: (Eq k, Hashable v) => Build Monad [Trace k v] k v
shake = recursive $ \key fetch act -> do
    traces <- gets (getInfo . fst)
    poss <- traceMatch (\k v -> (==) v . hash <$> fetch k) key traces
    current <- gets (getHash key . fst)
    when (current `notElem` poss) $ do
        (v, ds) <- act
        modify $ \(s, done) ->
            let t = Trace key [(d, getHash d s) | d <- ds] (getHash key s)
            in (putInfo (t : getInfo s) (putValue key v s), done)

@@

Now we have seen all three dependency schemes, we can directly reuse \hs{topological} to define \Bazel. Furthermore, as \Bazel is a tracing build system, we can reuse \hs{Trace} and \hs{traceMatch}, along with the \hs{Traces} type from \S\ref{sec-constructive-traces}. With these pieces in place, the implementation of \Bazel is given in Figure~\ref{fig-bazel-implementation}. We first figure out the possible results given the current state. If there are no recorded traces for the current dependencies we run it and record the results, otherwise grab a result from the \hs{contents} cache.

The program presented above captures certain aspects of \Bazel, but the real implementation makes one important additional assumption on \hs{Task} -- namely that it is \textit{deterministic}. With that assumption \Bazel is able to create the result hash in a trace by hashing together the result hashes of the dependencies and the key -- as the mapping between dependencies and results is deterministic. That change can be reflected in the code above by storing an additional \hs{Map k (Hash v)} which records the single most-recent

 rather than adding \hs{getHash key s} to the trace, \Bazel adds a hash of the dependencies hashes

more accurately describes \CloudBuild \cite{cloudbuild} - both \Bazel and the closely related \Buck make the assumption that builds are \textit{deterministic}, and thus that
